---
title: "hwk10"
author: "blair christensen"
date: "3/30/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# 1. Using a for loop, write a function to calculate the number of zeroes in a numeric vector. Before entering the loop, set up a counter variable counter <- 0. Inside the loop, add 1 to counter each time you have a zero in the matrix. Finally, use return(counter) for the output.
```{r}
numvec<-function(n=10){
  vec=round(runif(n, min=-1, max=10))
  #vec<-c(0,0,0,0,1)
  k<-0
  for (i in vec) {
    ifelse(i==0,k<-k+1,k<-k+0) 
  }
  return(k)
}
numvec()
```
# 2. Use subsetting instead of a loop to rewrite the function as a single line of code.
```{r}
numvecB<-function(n=10){
  vec=round(runif(n, min=-1, max=10))
  #vec<-c(0,0,0,0,1)
  k<-(vec[vec==0])
  return(length(k))
}
numvecB()
```
# 3 Write a function that takes as input two integers representing the number of rows and columns in a matrix. The output is a matrix of these dimensions in which each element is the product of the row number x the column number.
```{r}
#mat<-matrix(nrow=i, ncol=j)
three<-function(i=3,j=3){
  mat <- matrix(nrow=i,ncol=j)
  for (i in 1:nrow(mat)) { #i is row
    for (j in 1:ncol(mat)) { #j is col
      (mat[i,j] <- i*j) # assign to the i*j
  } 
  }
  return(mat)
}  
three(3,3)
```
# 4 In the next few lectures, you will learn how to do a randomization test on your data. We will complete some of the steps today to practice calling custom functions within a for loop. Use the code from the March 31st lecture (Randomization Tests) to complete the following steps:

# 4a Simulate a dataset with 3 groups of data, each group drawn from a distribution with a different mean. The final data frame should have 1 column for group and 1 column for the response variable.

